---
title: "Acquisition"
author: "Arpita Anand Prayag"
format: html
editor: visual
---

# Acquisition Challenges

## Get some data via an API. There are millions of providers, that offer API access for free and have good documentation about how to query their service.

## Running Code

### Load libraries

```{r}
library(RSQLite)
library(dplyr)
library(httr)
library(glue)
library(jsonlite)
library(keyring)
library(rstudioapi)
library(rvest)
```

### Send the GET request to the API

```{r}
response <- GET("https://www.themealdb.com/api/json/v1/1/filter.php?c=Seafood")
```

### Check the status code

```{r}
if (response$status_code == 200) {
  # The request was successful
  # Get the response data

  meals_db <- response %>%
    .$content %>%
    rawToChar() %>%
    fromJSON()
  
  as.data.frame(meals_db)
} else {
  # The request failed
  print(response$status_code)
}
```

## Scrape one of the competitor websites of canyon

### Set the URL of the website to scrape

```{r}
url <- "https://www.rosebikes.de/"
```

### Scrape the website

```{r}
html <- read_html(url)

# Find the elements that contain the model names
model_names <- html %>%
  html_nodes(".products-slider-tile__product-name") %>%
  html_text()

# Find the elements that contain the prices
prices <- html %>%
  html_nodes(".product-tile-price__current-value") %>%
  html_text()

# Extract the number using regular expressions
price <- gsub("[^0-9.,]", "", prices)  # Remove all non-digit, non-decimal, and non-comma characters

```

### Create a data frame of the model names and prices

```{r}
database <- data.frame(
  Model = model_names,
  Price = price
)

database
```
